---
title: "01_make_data_"
output: pdf_document
date: "2023-09-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
install.packages("tidytuesdayR", repos = "https://cran.rstudio.com/")
```
## Section 1
In this project, I would like to analyze a horror movie data set. The data consists of approximately 35,000 titles since the 1950s with 20 co-variates. I want to know whether there is a particular month of the year that horror movies outperform other months in terms of revenue, popularity, or rating.

## Section 2
My killer graph will be a bar graph consisting of three bars per month. One bar for averages of revenue, popularity, and rating. This way I can see whether there is a preferred month to release a horror movie, something movie producers would be interested in.


## Section 3

```{r}
tuesdata <- tidytuesdayR::tt_load('2022-11-01')
```
## Section 4
```{r}
dim(tuesdata$horror_movies)
```
## Section 5
```{r}
save.image()
```

