---
title: "02_EDA"
output: pdf_document
date: "2023-09-16"
---
```{r}
tuesdata <- tidytuesdayR::tt_load('2022-11-01')
data <- tuesdata$horror_movies
```
## Section 1
The response variables I'm interested in are revenue, popularity, and rating.
```{r}
par(mfrow=c(1,3))
revhist <- hist(data$revenue)
pophist <- hist(data$popularity)
rathist <- hist(data$vote_average)
par(mfrow=c(1,1))
```
```{r}
par(mfrow=c(1,3))
revboxplot <- boxplot(data$revenue)
popboxplot <- boxplot(data$popularity)
ratboxplot <- boxplot(data$vote_average)
par(mfrow=c(1,1))
```
## Section 2
The explanatory variable I'm interested in is month of release.
```{r}
#install.packages("lubridate")
library(lubridate)
```
```{r}
df <- data.frame(release_date = as.Date(data$release_date))
df$monthname <- month(df$release_date, label = TRUE)
df$month <- month(df$release_date)
hist(df$month)
```
## Section 3
After considering the variables further and previous documentation, I'm not sure what the popularity variable measures. Certainly, it should say that a higher number means the movie was more popular, but in what sense? Therefore, I will not be including it as on of my response variables in my killer graph.
```{r}
#install.packages("dplyr")
library(dplyr)
```

```{r}
data$month <- df$monthname
result <- data %>%
  group_by(month) %>%
  summarise(mean_revenue = mean(revenue, na.rm = TRUE), mean_rating = mean(vote_average, na.rm = TRUE))
print(result)
barplot(as.numeric(as.matrix(result)[,2]),names.arg = as.matrix(result)[,1],main = "Bar Chart of Average Monthly Revenue",xlab = "Month",ylab = "Average Revenue")
barplot(as.numeric(as.matrix(result)[,3]),names.arg = as.matrix(result)[,1],main = "Bar Chart of Average Monthly Rating",xlab = "Month",ylab = "Average Rating")

```
## Section 4
```{r}
save.image()
```

